Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-10 article/ms.tex
edits

NGC 2419 is the Milky Way's third most massive globular cluster, and its chemical composition makes it perhaps the most unusual star cluster in the Galaxy.

A spectroscopic study of RGB giant stars in NGC 2419 led to the discovery discovery of a strong anti-correlation between Mg and K in around 30-40 \% of the studied stars, along with weaker relations in Si, Sc, Ca, Ti and V (\citet{mucciarelli2012}, \citet{cohenkirby2012}). Depletions of Mg within globular clusters are not uncommon, but are always accompanied with an increase in [Fe/H]. The mechanism for this phenomena is the introduction of $\alpha$ poor but iron rich material released from Type Ia supernovae locally polluting the 'normal' [Mg/Fe] material released from Type II supernovae. However, the two sub-populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}. Further, Type Ia supernovae enrichment does not account for the enhanced K abundance or trends in the other elements.

Recently \cite{youngwooklee} used a Ca filter to identify two population in NGC 2419 corresponding to two generations of stars: G1, first generation metal poor stars, and G2, second generation stars displaying enhanced Ca and significantly increased He abundance ($\Delta Y = 0.19$). The Mg depleted population identified previously was found to be contained with the G2 population.

@@

At present, there is no accepted nuclear process that can explain the elemental abundance in NGC 2419. The fact that the Mg-K anti-correlation is confined to these very few specific globular clusters would seem to imply either a small population  of unusual polluter stars of some sort or a single extremely massive polluter star.

@@

>>>>

NGC 2419 is the Milky Way's third most massive globular cluster, and its chemical composition makes it perhaps the most unusual star cluster in the Galaxy. Recent spectroscopic studies of red giant branch (RGB) stars in NGC 2419 revealed a strong anti-correlation between Mg and K abundances in nearly half of the studied stars, and weaker abundance relations in Si, Sc, Ca, Ti and V \citep{mucciarelli2012,cohenkirby2012}. Depletions of Mg within globular clusters are not uncommon, but are always accompanied with an increase in [Fe/H] \todo{[citations needed; possibly remove]}. One mechanism for this phenomena is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae which locally pollutes the more `normal' [Mg/Fe] ratios that arise from Type II supernovae. However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}. Furthermore, Type Ia supernovae enrichment cannot account for the enhanced K abundance or the similar  abundance trends observed in NGC 2419.

Currently there is no known nuclear process that can explain the abundance variations in NGC 2419 without invoking unrealistic temperature conditions or by altering reaction rates by several orders of magnitude.

%Recently \cite{youngwooklee} used a Ca filter to identify two population in NGC 2419 corresponding to two generations of stars: G1, first generation metal poor stars, and G2, second generation stars displaying enhanced Ca and significantly increased He abundance ($\Delta Y = 0.19$). The Mg depleted population identified previously was found to be contained with the G2 population.

@@

@@

The fact that the Mg-K anti-correlation is confined to these very few specific globular clusters would seem to imply either a small population  of unusual polluter stars of some sort or a single extremely massive polluter star.
